Understanding GDP relations to Crime in US Cities

### 2017-03-07 resource/index.Rmd
add new gdp data and melt stuff

The data that we used in this anaylsis is combination of a data set that has crime in US cities over a 5 year time persion (2010-2015) and the GDP for cities in the same time period.

>>>>

The data that we used in this anaylsis is a combination of a data set that has crime in US cities over a 5 year time period (2010-2015) and the GDP for cities in the same time period.
